### 2022-10-13 README.Rmd
update

df <- haven::read_sav("Study 1.sav") |> 
  mutate_all(as.numeric) |> 
  mutate(Gender = as.character(ifelse(Gender == 1, "Male", "Female")))

@@

@@

@@

graph_data <- tidySEM::prepare_graph(cfa5mod, 
                   layout=get_layout(cfa5mod, layout_algorithm = "layout_with_kk"), 
                   variance_diameter=NA)

>>>>

df <- haven::read_sav("Study 1.sav") |> 
  mutate_all(as.numeric) |> 
  mutate(Gender = as.character(ifelse(Gender == 1, "Male", ifelse(Gender == 2, "Female", "Other"))))

@@

## New sample

```{r, message=FALSE, warning=FALSE, results='asis'}
df2 <- haven::read_sav("Study 6 IAS.sav") |> 
  mutate_all(as.numeric) |> 
  mutate(Gender = as.character(ifelse(Gender == 1, "Male", ifelse(Gender == 2, "Female", "Other"))))

paste0(
  "Data from the [study 6](https://osf.io/3m5nh/?view_only=a68051df4abe4ecb992f22dc8c17f769) (Murphy et al., 2020), downloaded from OSF, included ",
  report::report_participants(df2, age = "Age", sex = NA, gender = "Gender"),
  "."
)
```

```{r, message=FALSE, warning=FALSE}
cfa5mod_refit <- update(cfa5mod, data=df2)
cfa5_refit <- update(cfa5, data=df2)
cfa4mod_refit <- update(cfa4mod, data=df2)

anova(cfa5mod_refit, cfa5_refit, cfa4mod_refit)
```

@@

```{r, message=FALSE, warning=FALSE}
final <- update(cfa5mod, data = datawizard::data_merge(df, df2, join="bind"))
```

@@

graph_data <- tidySEM::prepare_graph(cfa5mod, 
                   layout=get_layout(cfa5mod, layout_algorithm = "layout_nicely"), 
                   variance_diameter=NA)
